Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-10 paper.qmd
Removed unncessary code

@@

pixels_gathered_within <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_right_top)

@@

pixels_gathered_within <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_middle)

@@

pixels_gathered_within <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_right_bottom)

@@

pixels_gathered_outside <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_error_outside)

@@

##### inside
img_error_inside <- c(3179, 7363, 7650, 5241, 5173, 6981, 7228, 6673, 4636) #7228, 7363, 7650

pixels_gathered_inside <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_error_inside)

>>>>

mnist_data <- mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28)

@@

pixels_gathered_within <-  mnist_data |>
  filter(instance %in% img_right_top)

@@

pixels_gathered_within <-  mnist_data |>
  filter(instance %in% img_middle)

@@

pixels_gathered_within <-  mnist_data |>
  filter(instance %in% img_right_bottom)

@@

pixels_gathered_outside <-  mnist_data |>
  filter(instance %in% img_error_outside)

@@

##### inside
img_error_inside <- c(3179, 7363, 7650, 5241, 5173, 6981, 7228, 6673, 4636)

pixels_gathered_inside <-  mnist_data |>
  filter(instance %in% img_error_inside)
